---
output: github_document
always_allow_html: true
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# datamanager

<!-- badges: start -->

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.xxxxxxx.svg)](https://doi.org/10.5281/zenodo.xxxxxxx)
[![codecov](https://codecov.io/gh/annyg/datamanager/branch/main/graph/badge.svg)](https://codecov.io/gh/annyg/datamanager)
![License:GPL-3.0](https://img.shields.io/badge/license-GPL--3.0-green.svg)

<!-- badges: end -->

`datamanager` is an R package designed for the efficient management and
scoring of research data, particularly focusing on questionnaire and
survey data. It provides a suite of functions to handle common tasks in
data preparation and scoring, including support for instruments such as
RAND-12 and EMQ.

## Features

-   **Data Management**: Effortlessly clean and organize questionnaire
    data.
-   **Scoring Functions**: Compute scores for recognized instruments
    including RAND-12 and EMQ.
-   **Efficient Workflow**: Streamline your data processing tasks in
    research settings.

## Installation

You can install the latest version of `datamanager` directly from GitHub
using:

```{r, message=FALSE}
if (!require("pak")) install.packages("pak")
pak::pak("annyg/datamanager")
library(datamanager)
```

## Usage

The `datamanager` package is designed to handle data frames and
primarily builds on tidyverse syntax. Below are examples demonstrating
how to use the main functions in `datamanager`.

### Data Management

```{r message=FALSE}
#library(datamanager)

# Example function call for cleaning common typos often found in email adresses
# cleaned_df <- df %>%
#   mutate(clean_emails = datamanager::prep_email(messy_emails))
```

### Scoring Instruments

#### RAND-12 Scoring

```{r}
# Example for scoring RAND-12
# rand12_scores <- score_rand12(cleaned_data)
```

#### EMQ Scoring

```{r}
# Example for scoring EMQ
# emq_scores <- score_emq(cleaned_data)
```

For detailed documentation on these functions and more, please refer to
the package help files or vignette.

## Citation

If you use `datamanager` in your research, please cite it as follows:

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.xxxxxxx.svg)](https://doi.org/10.5281/zenodo.xxxxxxx)

Example BibTeX entry:

```{bibtex}
@software{Anders B. Nygaard_2023_XXXXXXX,
  author       = {Anders B. Nygaard},
  title        = {datamanager: Tools for Questionnaire and Survey Data Management},
  month        = month,
  year         = 2023,
  publisher    = {GitHub},
  journal      = {GitHub repository},
  version      = {v1.0.0},
  doi          = {10.5281/zenodo.xxxxxxx},
  url          = {https://github.com/annyg/datamanager}
}
```

## Lifecycle

This package is currently an experimental, as defined by the [RECON
software lifecycle](https://www.reconverse.org/lifecycle.html). This
means that it is functional, but interfaces and functionalities may
change over time, testing and documentation may be lacking.

## Contributing

We welcome contributions! If you’d like to contribute to `datamanager`,
please fork the repository, create a branch, and submit a pull request.

## License

`datamanager` is licensed under the GNU General Public License v3.0. See the `LICENSE` file for more information.


------------------------------------------------------------------------

We hope you find `datamanager` useful in your research projects. For any
questions, issues, or suggestions, please open an issue on GitHub or
contact us.
